Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-23 conclusions.tex
Minor corrections to conclusion
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1144 ccdd05d5-56c1-461a-bf98-85f6876523b4

The detection algorithm we described has no intrinsic latency.  However, there
are fundamental and practical latencies associated with the analysis and
detection procedure. For example, the \LIGO{} data acquisition records science
data in 1/16~s blocks~\citep{Bork2001}. Data must also be aggregated from all
of the \GW\ observatories using global computer networks capable of high
bandwidth but perhaps only modest latency.  This could introduce a latency of
$\sim$100~ms.  Lastly, the software implementation of the algorithm itself may
introduced latency.  We have shown prototype implementation of \lloid{} using
the open source signal processing platform \gstreamer. Significant work would
have to be done in order to improve upon the latency of our implementation,
including tighter integration between data acquisition and analysis. This could
be considered for third-generation detector design.  Also possible for
third-generation instruments, the \lloid{} method could provide the input for a
dynamic tuning of detector response via the signal recycling mirror to match
the frequency of maximum sensitivity to the instantaneous frequency of the
\GW{} waveform.  This is a challenging technique, but it has the potential for
vast gains in \SNR{} and timing accuracy \citep{PhysRevD.47.2184}.

>>>>

The detection algorithm we described has no intrinsic latency.  However, there
are fundamental and practical latencies associated with the analysis and
detection procedure. For example, the \LIGO{} data acquisition records science
data in 1/16~s blocks~\citep{Bork2001}. Data must also be aggregated from all
of the \GW\ observatories using global computer networks capable of high
bandwidth but perhaps only modest latency.  This could introduce a latency of
$\sim$100~ms.  Lastly, the software implementation of the algorithm itself may
introduce latency.  We have shown a prototype implementation of \lloid{} using
\gstreamer, an open source signal processing platform. Some work could
be done in order to improve upon the latency of our implementation,
including tighter integration between data acquisition and analysis. This could
be considered for third-generation detector design.  Also possible for
third-generation instruments, the \lloid{} method could provide the input for a
dynamic tuning of detector response via the signal recycling mirror to match
the frequency of maximum sensitivity to the instantaneous frequency of the
\GW{} waveform.  This is a challenging technique, but it has the potential for
vast gains in \SNR{} and timing accuracy \citep{PhysRevD.47.2184}.
